---
title: "Session 6"
output: html_notebook
---
# Part 1 Preparation

## Identify  and list the correct files
Create a list of all data files in the .csv folder
```{r}
files.list <- list.files(path= "s6data//",  # Folder in R project
                         recursive=T,       # recursive extension
                         pattern='*.csv')   # get files list from folder
files.list                                  # list object name
```

## Appending file list:
Append the appropriate file path to the csv list, so I don't have to open a new folder etc. We can do this using a for loop:
```{r}
for(i in 1: length(files.list)){
  file.list <- paste("s6data//",files.list, sep="")
  return(file.list)
}
```


## `empty_as_na()` 
Due to the uniquely messy PsychoPy2 output file, I created the following function to fill empty cells in a data subset: I partition for `Set A` data and then fill all the empty columns with `na`, then delete all columns with `na` as contents. This can be accompished basing our custom function on an ifelse statement

```{r}
#Custom empty function
empty_as_na <- function(x){
  if("factor" %in% class(x)) x <- as.character(x) ## since ifelse wont work with factors
  ifelse(as.character(x)!="", x, NA)
}
```

## Set options
```{r}
options(scipen = 999,                 # remove scientific notation
        stringsAsFactors = FALSE)     # stops auto Factoring
set.seed(42)                          # for random Numbers
```

## Load necessary packages
```{r}
#install.packages("janitor")
source("StdScorePlot.R") # For Std Score Plots
library(janitor)
library(reshape2)
library(viridis)
library(tidyverse)
```

# 2) Main For loop
The same set of functions are applied 5 times (once for each set), participant details ae extracted.

For the `for loop` to work, we need to initialise empty data frames for our processed data to fill up
```{r}
# Initialise an empty dataframes to fill in the processing loop
d   <- NULL # Test Data 
TD  <- NULL # Test Details
```

This is the main processing loop:
```{r}
# For loop to clean and arrange data
for(j in 1: length(file.list)){
  
  # data
  data <- read.csv(file.list[j])
  
  # Test details
  data %>%
    select(participant, expName, date, frameRate) ->> td
  td  <- td[1,]
  TD  <- rbind(TD, td)
  #### SET A ###########################
  a_set <- data[1:12,]
  
  # empty na function
  a_set %>%
    mutate_all(funs(empty_as_na)) %>%
    remove_empty(which="cols") ->> TestA
  
  # Rename the A images coded properly
  TestA %>%
    select(participant,
           contains("images", ignore.case = TRUE), 
           contains("Index", ignore.case = TRUE),
           contains("rans", ignore.case = TRUE),
           contains(".keys", ignore.case = FALSE),
           contains(".cor", ignore.case = FALSE),
           contains(".rt", ignore.case = FALSE))->> TestA.f
  
  # rename Cols
  names(TestA.f)[2:7] <- c("Item", "Index", "Corrans", "Key_Raw", "Score", "RT")
  
  # Reorder by The item Index
  TestA.g <- TestA.f[order(TestA.f$Index), ]
  
  suffix <- seq(1:12)# For renaming/numbering
  
  # this pastes for a regex
  TestA.g$Item<- paste("A", 
                       formatC(suffix, width=2, flag="0"), sep="_")
  
  # Separate into two DFs for melt
  TestA.g %>%
    select(participant, Item, Corrans,  Key_Raw, Score, RT) ->> TestA.h
  
  #### SET B ###########################
  b_set <- data[13:24,]
  
  # Remove empty cells
  b_set %>%
    mutate_all(funs(empty_as_na)) %>%
    remove_empty(which="cols") ->> TestB
  
  # Now Rename the A images coded properly
  TestB %>%
    select(participant,
           contains("images", ignore.case = TRUE), 
           contains("Index", ignore.case = TRUE),
           contains("rans", ignore.case = TRUE),
           contains(".keys", ignore.case = FALSE),
           contains(".cor", ignore.case = FALSE),
           contains(".rt", ignore.case = FALSE))->> TestB.f
  #expName, Gender, frameRate, Sex, LevelEducation, session, date, Nationality,
  # rename Cols
  names(TestB.f)[2:7] <- c("Item", "Index", "Corrans", "Key_Raw", "Score", "RT")
  # Reorder by The item Index
  TestB.g <- TestB.f[order(TestB.f$Index), ]
  ###
  suffix <- seq(1:12)# For renaming/numbering
  
  # this pastes for a regex
  TestB.g$Item<- paste("B", formatC(suffix, width=2, flag="0"), sep="_") 
  
  # Separate into two DFs for melt
  TestB.g %>%
    select(participant,Item, Corrans,  Key_Raw, Score, RT) ->> TestB.h
  
  #############################################
  c_set <- data[25:36, ]
  c_set %>%
    mutate_all(funs(empty_as_na)) %>%
    remove_empty(which="cols") ->> TestC
  #############################################
  # Now Rename the A images coded properly
  TestC %>%
    select(participant,
           contains("images", ignore.case = TRUE), 
           contains("Index", ignore.case = TRUE),
           contains("rans", ignore.case = TRUE),
           contains(".keys", ignore.case = FALSE),
           contains(".cor", ignore.case = FALSE),
           contains(".rt", ignore.case = FALSE))->> TestC.f
  # rename Cols
  names(TestC.f)[2:7] <- c("Item", "Index", "Corrans", "Key_Raw", "Score", "RT")
  # Reorder by The item Index
  TestC.g <- TestC.f[order(TestC.f$Index), ]
  ###
  suffix <- seq(1:12)# For renaming/numbering
  TestC.g$Item<- paste("C", formatC(suffix, width=2, flag="0"), sep="_")
  # Separate into two DFs for melt
  TestC.g %>%
    select(participant,Item, Corrans,  Key_Raw, Score, RT) ->> TestC.h
  
  ##############################################
  d_set <- data[37:48, ]
  d_set %>%
    mutate_all(funs(empty_as_na)) %>%
    remove_empty(which="cols") ->> TestD
  #############################################
  # Now Rename the A images coded properly
  TestD %>%
    select(participant,
           contains("images", ignore.case = TRUE), 
           contains("Index", ignore.case = TRUE),
           contains("rans", ignore.case = TRUE),
           contains(".keys", ignore.case = FALSE),
           contains(".cor", ignore.case = FALSE),
           contains(".rt", ignore.case = FALSE)
           )->> TestD.f
  # rename Cols
  names(TestD.f)[2:7] <- c("Item", "Index", "Corrans", "Key_Raw", "Score", "RT")
  # Reorder by The item Index
  TestD.g <- TestD.f[order(TestD.f$Index), ]
  ###
  suffix <- seq(1:12)# For renaming/numbering
  TestD.g$Item<- paste("D", formatC(suffix, width=2, flag="0"), sep="_") # this pastes for a regex

  # Separate into two DFs for melt
  TestD.g %>%
    select(participant, Item, Corrans,  Key_Raw, Score, RT) ->> TestD.h

  ###############################################
  e_set <- data[49:60, ]
  e_set %>%
    mutate_all(funs(empty_as_na)) %>%
    remove_empty(which="cols") ->> TestE
  #############################################
  # Now Rename the A images coded properly
  TestE %>%
    select(participant,
           contains("images", ignore.case = TRUE), 
           contains("Index", ignore.case = TRUE),
           contains("rans", ignore.case = TRUE),
           contains(".keys", ignore.case = FALSE),
           contains(".cor", ignore.case = FALSE),
           contains(".rt", ignore.case = FALSE))->> TestE.f
  # rename Cols
  names(TestE.f)[2:7] <- c("Item", "Index", "Corrans", "Key_Raw", "Score", "RT")
  # Reorder by The item Index
  TestE.g <- TestE.f[order(TestE.f$Index), ]
  ###
  suffix <- seq(1:12)# For renaming/numbering
  TestE.g$Item<- paste("E", formatC(suffix, width=2, flag="0"), sep="_") 
  # Separate into two DFs for melt
  TestE.g %>%
    select(participant, Item, Corrans,  Key_Raw, Score, RT) ->> TestE.h
  
  # Bind the data together
  x  <- rbind(TestA.h, 
              TestB.h, 
              TestC.h, 
              TestD.h, 
              TestE.h)
  
  # Add newly processed row to blank dataframe
  d  <-  rbind(d, x) # d is the output
}
```

Now we can check out our dataframe
```{r}
d
```
Create a new variable for the Set each item belongs to
```{r}
d$Set <- substr(d$Item, 0, 1)
```

Change the participant, Item, Set, Corrans, Key_Raw and Score columns to a factor
```{r}
cols_d  <-  c("participant", "Item", "Set", "Corrans", "Key_Raw") # For desired cols

d %>%
  mutate_at(cols_d, funs(factor(.))) ->> d2

d2
```


# 3 Plot the Data
```{r}
d2 %>%
  ggplot(aes(x = RT, group = participant, fill=participant))+
  geom_histogram(colour = "grey22")+
  facet_wrap(participant~Score)+
  theme_classic()+
  xlab("Response Time")+
  scale_fill_viridis(discrete = TRUE, guide=guide_legend(nrow=2))+
  labs(fill = "Participant")+
   theme(strip.text = element_text(size = 8,
                                   face = "bold"),
         strip.background = element_blank()) ->> FacetRT
FacetRT
```


Summarise data
```{r}
d2 %>%
  group_by(participant) %>%
  summarise(Total = sum(Score), 
            Prop.Correct = (Total/60),
            RT.avg = mean(RT)) ->> Sum.tdy

Sum.tdy
```

#4) Standard Score Plot
```{r}
standardScorePlot1(lb  = 55, 
                  ub  = 145,
                  lb1 = 70, 
                  ub1 = 130, 
                  lb2 = 80, 
                  ub2 = 120, 
                  lb3 = 90, 
                  ub3 = 110,
                  lb4 = 99.75,
                  ub4 = 100.25)+
  theme_classic() + coord_fixed(ratio=1700) +
  theme(axis.text.x = element_text(colour="black", size="6"),
        axis.line.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank(),
        legend.position="none") ->> ScorePlot1

ScorePlot1
```

```{r}
standardScorePlot2(lb  = 55, 
                  ub  = 145,
                  lb1 = 70, 
                  ub1 = 130, 
                  lb2 = 80, 
                  ub2 = 120, 
                  lb3 = 90, 
                  ub3 = 110,
                  lb4 = 99.75,
                  ub4 = 100.25)+
  theme_classic() + coord_fixed(ratio=1700) +
  theme(axis.text.x = element_text(colour="black", size="6"),
        axis.line.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank(),
        legend.position="none") ->> ScorePlot2

ScorePlot2
```

If we want to place our Participant scores on the std score plot
First we needto add a colum with a standard score
```{r}
Sum.tdy$StdScore <- c(55, 
                      55, 
                      55)
```

Then We need to figure out the y-axis location to place the participant on the curve
```{r}
pg <- ggplot_build(ScorePlot)
#pg
```

This is the coordinate data produced during the plot generation for y-axis values. This will return probability values so Participant scores can be plotted on the Distribution curve (Aesthetic considerations) using geom_layer
```{r}
pg$data[[1]] ->> Plotdata
Plotdata
```

As it turns the PDF function value is `0.000343353866` for all three participants,
We know this will be messy so we can add a value
```{r}
Sum.tdy$Prob  <- c(0.000343353866,
                   0.005743353866,
                   0.011043353866)
Sum.tdy
```

And now we can plot adding our new data to the `ScorePlot` object
```{r}
ScorePlot1+
  geom_point(data = Sum.tdy, aes(x = StdScore, y = Prob, fill = participant),
             size = 6,
             shape = 21)
  
```

